---
title: "liber package features"
author: "Piotr Liberadzki"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

The aim of this document is to introduce user with some capabilities of liber package which has been created as a result of homework 6 from Advanced Data Analysis Software Development with R course.  

There will be described three functions of **liber** package:

* mode
* simplify2array1
* ass

First step is of course installing and loading **liber** package.Then it is possible to use mentioned functions. 

```{r,echo=T,warning=FALSE,error=FALSE,message=FALSE}
library(liber)
```


**Mode()**


Function mode() determines the most frequently occurring value in an integer vector. Mode() takes an integer vector and returns integer values which occures most frequently. 

Examplary use mode() function:

```{r,echo=T,warning=FALSE,error=FALSE,message=FALSE}
mode(c(2,2,5,1,4,5,1,90,5))
mode(c(1:10,1))
mode(1)
```


**simplify2array1()**


Function simplify2array1() mimic the behaviour of simplify2array() R function.
If the dimensions of input numeric vectors from list are equal function transforms vectors into one numeric matrix. Otherwise function throws an error.

Examplary use simplify2array1() function:

```{r,echo=T,error=TRUE}
simplify2array1(list(c(1,2,3),c(1,2,3),c(1,2,2)))
simplify2array1(list(2))
simplify2array1(list(c(1,2,3),c(1,2,3),c(1,2)))
```


**ass()**


Function ass() for some given integer n generates all possible 0-1 assignment
vectors of 2n survey participants in such a way that exactly n of them are assigned to group 0 (control) and the other n ones are assigned to group 1 (treatment). Ass() returns a matrix with 2n columns and an appropriate number of rows. 

Examplary use ass() function:

```{r,echo=T,error=TRUE}
ass(1)
ass(2)
ass(3)
```
